A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-09-06 paper/elsarticle/elsarticle-template.tex
paper

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene~\cite{schlund2018moglichkeiten,uva2018evaluating,masood2019augmented,gattullo2019towards,aschenbrenner2019comparing,mayrhofer2019one,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to such instructions in paper form or on a statically situated screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed typically using some form of handheld or head-mounted display. Handheld devices such as tablets do not enable the user to work hands-free while using the device, or force the user to wear additional gear. Reliance on head-mounted displays has two adverse consequences of its own: a head-mounted display must be worn by each individual wishing to partake in the augmentation, and such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. A Hololens 2, for instance, is such a head-mounted display; at a weight of 566~grams,\footnote{\url{https://www.microsoft.com/en-us/hololens/hardware}} it places an additional ergonomic load on the worker, in particular if worn over a longer duration or in bent positions.

In turn, a form of augmented reality referred to as \textit{spatial} AR\cite{bimber2019spatial} is carried out not by embedding the augmentation in an image of the scene as with a head-mounted or handheld display, but by projection to the scene itself, thus eliminating the aforementioned problems. Spatial AR thus turns surfaces such as the product being manufactured, a desk, the floor, a wall, or even the ceiling (considering overhead work) into displays. Information provision---of the work plan or of quality-related information---can be can be carried out by projection to the given workspace, while directly referring to exact positions within that workspace. Moreover, the fact that this information can be viewed by multiple users simultaneously serves to promote collaboration \cite{aschenbrenner2019comparing}.

>>>>

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene~\cite{schlund2018moglichkeiten,uva2018evaluating,masood2019augmented,gattullo2019towards,aschenbrenner2019comparing,mayrhofer2019one,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to such instructions in paper form or on a statically situated screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed typically using some form of handheld or head-mounted display. Handheld devices such as tablets do not enable the user to work hands-free while using the device, or force the user to wear additional gear. Reliance on head-mounted displays has two adverse consequences of its own: a head-mounted display must be worn by each individual wishing to partake in the augmentation, and such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. A HoloLens 2, for instance, is such a head-mounted display; at a weight of 566~grams \cite{hololens}, it places an additional ergonomic load on the worker, in particular if worn over a longer duration or in bent positions.

In turn, a form of augmented reality referred to as \textit{spatial} AR\cite{bimber2019spatial} is carried out not by embedding the augmentation in an image of the scene as with a head-mounted or handheld display, but by projection to the scene itself, thus eliminating the aforementioned problems. Spatial AR thus turns surfaces such as the product being manufactured, a desk, the floor, a wall, or even the ceiling (considering overhead work) into displays. Information provision---of the work plan or of quality-related information---can be carried out by projection to the given workspace, while directly referring to exact positions within that workspace. Moreover, the fact that this information can be viewed by multiple users simultaneously serves to promote collaboration \cite{aschenbrenner2019comparing}.
